\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-07-21 article.tex
explain not from ggenealogy plot

\begin{figure}[H]
    \centering
    \fbox{\includegraphics[width=\textwidth]{LeeAD}}
    \caption{Top: All ancestors and descendants of the variety \code{Lee} are shown in this \pkg{ggenealogy} plot. Bottom: We now attempt to mimic the blue paths in the \pkg{ggenealogy} plot on the top, only now nodes cannot be repeated. The parenthetical numbers above each node represents the set of generation counts that node is away from the center node \code{Lee}. The presence of red parentheses indicate that the plot on the bottom ambiguously display the example soybean genealogy in the way that the \pkg{ggenealogy} plot on the top can accomplish.}
    \label{fig:Lee}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \fbox{\includegraphics[width=\textwidth]{LeeAD}}
    \caption{Top: All ancestors and descendants of the variety \code{Lee} are shown in this \pkg{ggenealogy} plot. Bottom: This plot was constructed manually outside of the \pkg{ggenealogy} plot for didactic purposes. It mimics the blue paths in the \pkg{ggenealogy} plot on the top, only now nodes cannot be repeated. The parenthetical numbers above each node represents the set of generation counts that node is away from the center node \code{Lee}. The presence of red parentheses indicate that the plot on the bottom ambiguously display the example soybean genealogy in the way that the \pkg{ggenealogy} plot on the top can accomplish.}
    \label{fig:Lee}
\end{figure}
